Personal Research and Articles

### 2024-05-09 articles.qmd
Update
Update

<p> Educators like Mrs. Tan, Jeremy's guidance counselor, emphasize the importance of understanding each student's context. "We need to look beyond the behavior to the person behind it. Only then can we truly help," she notes. Mrs. Tan advocates for a system that prioritizes supportive measures over punitive ones, suggesting, "Reintegration, not isolation, is key to turning lives around."</p>

>>>>

<p> Educators like Mrs. Tan, Jeremy's guidance counselor, emphasize the importance of understanding each student's context. "We need to look beyond the behavior to the person behind it. Only then can we truly help," she notes. Mrs. Tan advocates for a system that prioritizes supportive measures over punitive ones, suggesting, "Reintegration, not isolation, is key to turning lives around." </p>
